resistanceModelNotesAndy

### 2016-03-01 resistanceModelNotesAndy.Rmd
notes

@@

~ checking on correctMixDeployProp
~ add correctMixDeployProp into curtis shiny UI to enable checking mechanism
~~ first add correctMixDeployProp into runcurtis_f2

~ carefully implement strategy name changes

>>>>

~ checking on correctMixDeployProp
~ added correctMixDeployProp into curtis shiny UI to enable checking mechanism
~~ first added correctMixDeployProp into runcurtis_f2

@@

~ carefully implement strategy name changes
Find & replace todo : in sensiAnPaper1All.Rmd & paper1_results_figs.Rmd

resistPointsMix2    resistPointsMix_A
resistPointsMix3    resistPointsMix_2
resistBetterMix2SeqBoolean  resistBetterMix_ASeqBoolean
resistBetterMix2Seq         resistBetterMix_ASeq

#### can I replace :
Mix1 - Mix_1
Mix2 - Mix_A
Mix3 - Mix_2
"Mixture 1" - "Mix either"
"Mixture 2" - "Mix adaptive"
"Mixture 3" - "Mix both"
done mix2_minus_seq0.25          mixA_minus_seq0.25

Long Names (in text where space not an issue)
Mixture (either insecticide)   
Mixture (both insecticides)
Adaptive mixture (both insecticides)
Sequential (both insecticides)

Medium Names (plot labels where medium space)
mix either              
mix both             
mix adaptive
sequential

Short Names (plot labels where v little space)
mix1
mix2
adapt
seq
